animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation

### 2025-07-11 animbook-journal.Rmd
address the NY Times figure comment

```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package. The animation illustrates the disparity between white men and black men. It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
knitr::include_graphics("figures/NYT.png")
```

>>>>

```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package. The animation illustrates the disparity between white men (yellow) and black men (blue). It reveals that despite black boys growing up in a rich household, they still have a higher likelihood of falling into lower income groups compared to white boys.This is observed by more yellow points apparently falling from the top bar to lower bars in the animated plot.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
knitr::include_graphics("figures/NYT.png")
```
